---
title: "Results, tables and graphs"
output:
  pdf_document:
    toc: yes
    highlight: tango
toc-title: Variables
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
wd <- ""

# if you wanted to run the analysis code (1000 iterations) change the 
# value of the variable doAll to TRUE. It may take a few minutes
doAll = FALSE
```

```{r , echo = FALSE}
pacman::p_load(gt, ROCR, kableExtra, ks, latex2exp)

load(paste0(wd, "results_analysis.RData"))
load(paste0(wd, "results_dist_diff.RData"))
load(paste0(wd, "example_coordinates.RData"))
setwd(wd)
```

```{bash , echo = FALSE, eval =  doAll}
./new_analysis.R
```

# Distribution of the polar coordinates 

An example (among the 1000 analyses performed) of the distribution
of the polar coordinates of the test set.

```{r , echo=FALSE, fig.height = 5, fig.width= 6}
plot(polar_coor[polar_coor$group == "model","theta"],
     polar_coor[polar_coor$group == "model","rho"],
     xlim = c(-0.7,0.7), ylim=c(0.5,0.85),
     col = as.numeric(polar_coor[polar_coor$group == "model", "response"]) + 3, 
     ylab=TeX(r"($r$)"), xlab=TeX(r"($\theta$)"))
legend("bottomleft", legend= c("Not Diagnosed", "Diagnosed"), fil = c(3,4))
```

# Density functions 

## Using the two polar coordinates

An example of the density functions.

- No diagnosed class (0)


```{r , echo = FALSE}
den_class0 <- kde(polar_coor[polar_coor$group == "model" 
                             & polar_coor$response == "0", c(1,2)])

image(den_class0$eval.points[[1]], den_class0$eval.points[[2]],
      den_class0$estimate, xlim = c(-0.8, 0.65), ylim = c(0.55, 0.95), 
      ylab=TeX(r"($r$)"), xlab=TeX(r"($\theta$)"))
```

- Diagnosed class (1)


```{r , echo = FALSE}
den_class1 <- kde(polar_coor[polar_coor$group == "model" 
                             & polar_coor$response == "1", c(1,2)])

image(den_class1$eval.points[[1]], den_class1$eval.points[[2]],
      den_class1$estimate, xlim = c(-0.8, 0.65), ylim = c(0.55, 0.95), 
      ylab=TeX(r"($r$)"), xlab=TeX(r"($\theta$)"))
```


## Using only the $\theta$ coordinate  

An example of the density functions.


```{r , echo = FALSE}
den_class0 <- density(polar_coor[polar_coor$group == "model" 
                                 & polar_coor$response == "0", "theta"], 
                      kernel = "epanechnikov")
den_class1 <- density(polar_coor[polar_coor$group == "model" 
                                 & polar_coor$response == "1", "theta"], 
                      kernel = "epanechnikov")

plot(NULL, xlim=c(-1,1), ylim=c(0,3), type="n", xlab=TeX(r"($\theta$)"),
     ylab=TeX(r"($f(\theta$|$y)$)"))
lines(den_class1, col="deepskyblue",type="p")
lines(den_class0,col="green",type="p")
text(-0.7, 2.5, "Diagnosed")
text(0.35,2.5, "Not Diagnosed")
```


# Average Confusion matrix

## Using the two polar coordinates 


```{r, echo= FALSE }
mean_two_cm <- round(apply(confusion_matrix_two_coor, 2, mean), digits = 4)

matrix <- cbind(c(mean_two_cm[1], mean_two_cm[3]), c(mean_two_cm[2], 
                                                     mean_two_cm[4]), 
                c("Real classification", "Real classification"), 
                c("Not diagnosed", "Diagnosed"))
colnames(matrix) = c("no_dx", "dx", "class", "names")
rownames(matrix) = c("Not diagnosed", "Diagnosed")

matrix  %>% gt(rowname_col = "names", groupname_col = "class") %>%
  cols_label(
    no_dx = md("Not diagnosed "),
    dx = md("Diagnosed")
  ) %>% 
  tab_spanner(label = "Predicted classification", columns = c(no_dx, dx)) 
```

## Using only the $\theta$ coordinate  
```{r, echo= FALSE }
mean_theta_cm <- round(apply(confusion_matrix_theta, 2, mean), digits = 4)

matrix <- cbind(c(mean_theta_cm[1], mean_theta_cm[3]), 
                c(mean_theta_cm[2], mean_theta_cm[4]), 
                c("Real classification", "Real classification"), 
                c("Not diagnosed", "Diagnosed"))
colnames(matrix) = c("no_dx", "dx", "class", "names")
rownames(matrix) = c("Not diagnosed", "Diagnosed")

matrix  %>% gt(rowname_col = "names", groupname_col = "class") %>%
  cols_label(
    no_dx = md("Not diagnosed "),
    dx = md("Diagnosed")
  ) %>% 
  tab_spanner(label = "Predicted classification", columns = c(no_dx, dx)) 
```

# ROC curve averaged using the vertical averaging method
## Using the two polar coordinates 

The ROC curve of 1000 analyses was averaged using the two coordinates as 
predictors. The bars show 95% confidence intervals.


```{r, echo= FALSE }
pred <- ROCR::prediction(dist_diff_two_coor$score, 
                         dist_diff_two_coor$class)
perf <- ROCR::performance(pred,'tpr','fpr')

ROCR::plot(perf,
     spread.estimate='stddev',
     avg='vertical',
     spread.scale=2, # to generate a confidence interval of approximately 95%
     col='black', ylab = "Average sensitivity", xlab = "1 - specificity")

AUC <- performance(pred, measure = "auc")
AUC_mean_two <- mean(as.numeric(AUC@y.values))
```


## Using only the $\theta$ coordinate  

The ROC curve of 1000 analyses was averaged using the $\theta$ coordinate 
as predictors. The bars show 95% confidence intervals. 


```{r, echo= FALSE }
pred <- ROCR::prediction(dist_diff_theta$score, 
                         dist_diff_theta$class)
perf <- ROCR::performance(pred,'tpr','fpr')

ROCR::plot(perf,
     spread.estimate='stddev',
     avg='vertical',
     spread.scale=2, # to generate a confidence interval of approximately 95%
     col='black', ylab = "Average sensitivity", xlab = "1 - specificity")

AUC <- performance(pred, measure = "auc")
AUC_mean_theta <- mean(as.numeric(AUC@y.values))
```

# Precision/Recall graph averaged using the vertical averaging method

## Using the two polar coordinates 

The Precision-Recall curve of 1000 analyses was averaged using the two coordinates
as predictors. The bars show 95% confidence intervals. 


```{r , echo = FALSE}
pred <- ROCR::prediction(dist_diff_two_coor$score, dist_diff_two_coor$class)
perf <- performance(pred, "prec", "rec")
plot(perf,
     spread.estimate='stddev',
     avg='vertical',
     spread.scale=2, # to generate a confidence interval of approximately 95%
     col='black', 
     ylab = "Average positive predictive value", xlab = "Sensitivity")
```

## Using only the $\theta$ coordinate 


The Precision-Recall curve of 1000 analyses was averaged using the $\theta$ 
coordinate as predictors. The bars show 95% confidence intervals. 


```{r, echo= FALSE }
pred <- ROCR::prediction(dist_diff_theta$score, dist_diff_theta$class)
perf <- performance(pred, "prec", "rec")
plot(perf,
     spread.estimate='stddev',
     avg='vertical',
     spread.scale=2, # to generate a confidence interval of approximately 95%
     col='black', 
     ylab = "Average positive predictive value", xlab = "Sensitivity")
```



# Average of other predictive parameters 

```{r, echo= FALSE}
mean_predict_value_two <- round(apply(prediction_parameters_two_coor, 2, mean), 
                           digits = 4)
mean_predict_value_two <- c(mean_two_cm["TP"], mean_two_cm["TN"], 
                            mean_predict_value_two, 
                            round(AUC_mean_two, digits = 4))

mean_predict_value_theta <- round(apply(prediction_parameters_theta, 2, mean), 
                            digits = 4)
mean_predict_value_theta <- c(mean_theta_cm["TP"], mean_theta_cm["TN"], 
                            mean_predict_value_theta, AUC_mean_theta)

names(mean_predict_value_two) <- c("Sensitivity", "Specificity", 
                                   "Negative Predictive Value", 
                                   "Positive predictive value", 
                                   "Accuracy", "F1 Score", 
                                   "Cohen's kappa coefficient",
                                   "Matthews correlation coefficient",
                                   "Area under the ROC curve")
names(mean_predict_value_theta) <- names(mean_predict_value_two)

table <- data.frame(mean_predict_value_two, mean_predict_value_theta)
colnames(table) <- c("Two coordinates", "$\theta$ coordinate only")
kable(table, col.names = c("Two coordinates", "Theta coordinate only"))
```


